### 2024-01-03 Paper/main.tex

\noindent
To train the network the DIV2K training and validation dataset was used. The dataset contains 800 train images and 100 test images. Since the images had different dimensions, we first had to crop them to specific in this case 512x512. Afterwards we compressed the images to specified file sizes as described in \ref{sec: filesize}. With the primary objectice beeing to recignize the different compression algorithms the output of the network should represent the different encoding schemes. This leads to 10 classes in each file size category.

@@

\noindent
After 10 epochs of training, we achieved a validation accuracy of 57,6 percent avaged over the 5 training filesizes (5, 10, 17, 25 and 32). For 10 epochs this is lower than the results we got for the transfer learning approach. However, if one would increase the number of epochs, we expect to reach the same levels of accuracy since the only defencemen is that the pretrained network has a preferable starting position compared to the one without transfer learning. This can be shown by changing the starting seed to something different leading to only 10 percent accuracy after 10 epochs.

>>>>

\noindent
To train the network the DIV2K training and validation dataset was used. The dataset contains 800 train images and 100 test images. Since the images had different dimensions, our first step was to crop all images to the same size in our case 512x512. Afterwards we compressed the images to specified file sizes as described in \ref{sec: filesize}. With the primary objectice beeing to recignize the different compression algorithms the output of the network should represent the different encoding schemes. This leads to 10 classes in each file size category.

@@

\noindent
After 10 epochs of training, we achieved a validation accuracy of 57,6 percent avaged over the 5 training filesizes (5, 10, 17, 25 and 32). For 10 epochs this is lower than the results we got for the transfer learning approach. However, if one would increase the number of epochs, we expect to reach the same levels of accuracy since the only difference is that the pretrained network has a preferable starting position compared to the one without transfer learning. This can be shown by changing the starting seed to something different leading to only 10 percent accuracy after 10 epochs.
